---
title: "Data Analysis"
author: "Amanda Gahlot"
date: "`r Sys.Date()`"
output: html_document
---


```{r prelims, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# Set up

```{r set wd, include=FALSE}
setwd("/Users/amandagahlot/Documents/Dissertation/Self_regulation")
```

```{r setup, include=FALSE}

#rm(list = ls(all = TRUE))  y


library(tidyverse)
library(psych)
library(data.table)
library(sjPlot) 
library(sjmisc) 
library(sjlabelled) 
library(gtsummary)
library(readxl)
```

## Import Data

```{r import, echo=FALSE, include=FALSE}

df <- read_excel('/Users/amandagahlot/Documents/Dissertation/R_Output/cleaned_data_Final.xlsx')

print(head(df))
```

# Tables by Severity

## Demographic  
The table below provides demographic information based on severity of injury

```{r demo df, echo=FALSE, include=FALSE}
df_demo <- df

```

```{r rename, echo=TRUE}
# level naming for categorical variables
df_demo$gender <- factor(df_demo$gender,
                   levels = c(1,2,3),
                   labels = c("Male", "Female", "Nonbinary"))

df_demo$work_current <- factor(df_demo$work_current,
                   levels = c(1,0),
                   labels = c("Yes", "No"))

df_demo$severity <- factor(df_demo$severity,
                   levels = c(2,3),
                   labels = c("Moderate", "Severe"))

df_demo$mech_injury <- factor(df_demo$mech_injury,
                   levels = c(1,2,3,4,5),
                   labels = c("Fall", "MVC", "Sports", "Violence", "Pedestrian struck"))

df_demo$income <- factor(df_demo$income,
                   levels = c(1,2,3),
                   labels = c("<52K", "52K-156K", ">156K"))

df_demo$marital_status <- factor(df_demo$marital_status,
                                 levels = c(1, 2, 3, 4),
                                 labels = c("Single", "Married", "Divorced", "Widowed"))

```

```{r table, results='asis', echo=FALSE, include=TRUE}
demo_table <- df_demo %>%
  subset(., select = c(age_current, time_injury, gender, edu, race, work_current, income, house_size, marital_status, substance, severity, mech_injury)) %>%
  tbl_summary(
    missing = "no",
    by = severity,
    type = list(
      c(age_current, edu, house_size, substance, time_injury) ~ "continuous",
      c(gender, income, work_current, severity, mech_injury) ~ "categorical"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)"),
    label = list(
      age_current ~ "Age (years)",
      time_injury ~ "Time since TBI (years)",
      gender ~ "Gender",
      race ~ "Race/Ethnicity",
      edu ~ "Education (years)",
      work_current ~ "Employment status",
      income ~ "Annual household income",
      house_size ~ "Size household",
      marital_status ~ "Marital status",
      substance ~ "Substance use score",
      mech_injury ~ "Cause of injury",
      severity ~ "Severity of Injury"
    )
  ) %>%
  add_p(
    test = list(all_continuous() ~ "t.test", all_categorical() ~ "chisq.test"),
    pvalue_fun = ~style_pvalue(.x, digits = 2)
  ) %>%
  add_n()

print(demo_table)   
```
```{r save table, echo=FALSE, include=FALSE}
#to save table to word doc
library(gt)
library(gtsummary)

gt_demo_table <- as_gt(demo_table)
   gtsave(gt_demo_table, filename = "demo_table_1.docx")
```

## ACS 
ACS3 (activity re-engagement scores - outcome measure) by severity of injury

```{r acs compare,  results='asis', echo=FALSE, include=TRUE}
acs_table <- df_demo %>%
  subset(., select = c(acsg_prev, acsg_curr, acsg_retain, acsi_prev, acsi_curr, acsi_retain, acsl_prev, acsl_curr, acsl_retain, acsf_prev, acsf_curr, acsf_retain, acss_prev, acss_curr, acss_retain, severity)) %>%
  tbl_summary(
    missing = "no",
    by = severity,
    type = list(
      c(acsg_prev, acsg_curr, acsg_retain, acsi_prev, acsi_curr, acsi_retain, acsl_prev, acsl_curr, acsl_retain, acsf_prev, acsf_curr, acsf_retain, acss_prev, acss_curr, acss_retain) ~ "continuous",
      c(severity) ~ "categorical"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)"),
    label = list(
      acsg_prev ~ "ACS Global Before",
      acsg_curr ~ "ACS Global Current",
      acsg_retain ~ "Global Retained (%)",
      acsi_prev ~ "ACS IADL Before",
      acsi_curr ~ "ACS IADL Current",
      acsi_retain ~ "IADL Retained (%)",
      acsl_prev ~ "ACS Leisure Before",
      acsl_curr ~ "ACS Leisure Current",
      acsl_retain ~ "Leisure Retained (%)",
      acsf_prev ~ "ACS Fitness Before",
      acsf_curr ~ "ACS Fitness Current",
      acsf_retain ~ "Fitness Retained (%)",
      acss_prev ~ "ACS Social Before",
      acss_curr ~ "ACS Social Current",
      acss_retain ~ "Social Retained (%)",
      severity ~ "Severity of Injury"
    )
  ) %>%
  add_p(
    test = list(all_continuous() ~ "t.test", all_categorical() ~ "chisq.test"),
    pvalue_fun = ~style_pvalue(.x, digits = 2)
  ) %>%
  add_n()

print(acs_table)   
```

```{r save tableACS, echo=FALSE, include=FALSE}
#to save table to word doc
library(gt)
library(gtsummary)

gt_acs_table <- as_gt(acs_table)
   gtsave(gt_acs_table, filename = "demo_table_ACS.docx")
```

Below is the ttest for the specific t and p value for the difference between ACS3 previous social score, which was significantly different.

```{r subset severity, echo=FALSE, include=TRUE}
#significant difference in ACSS between groups. t-test for t value
df_mod <- subset(df, severity == 2)
df_severe <- subset(df, severity == 3)
ttest_acsstotal <- t.test(df_mod$acss_prev, df_severe$acss_prev)
print(ttest_acsstotal)
```


## FrSBe
Comparison of self-regulation scores by severity

```{r frsbe compare,  results='asis', echo=FALSE, include=TRUE}
frsbe_table <- df_demo %>%
  subset(., select = c(frsbe_exec, frsbe_disinhib, frsbe_apathy, frsbe_total, severity)) %>%
  tbl_summary(
    missing = "no",
    by = severity,
    type = list(
      c(frsbe_exec, frsbe_disinhib, frsbe_apathy, frsbe_total) ~ "continuous",
      c(severity) ~ "categorical"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)"),
    label = list(
      frsbe_exec ~ "Executive function",
      frsbe_disinhib ~ "Disinhibition",
      frsbe_apathy ~ "Apathy",
      frsbe_total ~ "Total FrSBe Score",
      severity ~ "Severity of Injury"
    )
  ) %>%
  add_p(
    test = list(all_continuous() ~ "t.test", all_categorical() ~ "chisq.test"),
    pvalue_fun = ~style_pvalue(.x, digits = 2)
  ) %>%
  add_n()

print(frsbe_table)   
```

```{r save tableFrSBe, echo=FALSE, include=FALSE}
#to save table to word doc
library(gt)
library(gtsummary)

gt_frsbe_table <- as_gt(frsbe_table)
   gtsave(gt_frsbe_table, filename = "table_FrSBe.docx")
```

## TBI QOL
Comparison of subscales of TBI QOL measure by severity of injury

```{r table subscales TBIQOL, results='asis', echo=FALSE, include=TRUE}
tbiqol_table <- df_demo %>%
  subset(., select = c(tbiqol_part_sra_tscore, tbiqol_anger_tscore, tbiqol_anxiety_tscore, tbiqol_comm_tscore, tbiqol_depression_tscore, tbiqol_dyscontrol_tscore, tbiqol_execfunc_tscore, tbiqol_fatigue_tscore, tbiqol_genconcern_tscore, tbiqol_headache_tscore, tbiqol_mobility_tscore, tbiqol_pain_tscore, tbiqol_posaffect_tscore, tbiqol_resilience_tscore, tbiqol_satissra_tscore, tbiqol_selfesteem_tscore, tbiqol_stigma_tscore, tbiqol_ue_tscore, severity)) %>%
  tbl_summary(
    missing = "no",
    by = severity,
    type = list(
      c(tbiqol_part_sra_tscore, tbiqol_anger_tscore, tbiqol_anxiety_tscore, tbiqol_comm_tscore, tbiqol_depression_tscore, tbiqol_dyscontrol_tscore, tbiqol_execfunc_tscore, tbiqol_fatigue_tscore, tbiqol_genconcern_tscore, tbiqol_headache_tscore, tbiqol_mobility_tscore, tbiqol_pain_tscore, tbiqol_posaffect_tscore, tbiqol_resilience_tscore, tbiqol_satissra_tscore, tbiqol_selfesteem_tscore, tbiqol_stigma_tscore, tbiqol_ue_tscore) ~ "continuous",
      c(severity) ~ "categorical"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)"),
    label = list(
      tbiqol_part_sra_tscore ~ "Participation SRA",
      tbiqol_anger_tscore ~ "Anger",
      tbiqol_anxiety_tscore ~ "Anxiety",
      tbiqol_comm_tscore ~ "Communication",
      tbiqol_depression_tscore ~ "Depression",
      tbiqol_dyscontrol_tscore ~ "Dyscontrol ",
      tbiqol_execfunc_tscore ~ "EF",
      tbiqol_fatigue_tscore ~ "Fatigue",
      tbiqol_genconcern_tscore ~ "Gen Cognition",
      tbiqol_headache_tscore ~ "Headache",
      tbiqol_mobility_tscore ~ "Mobility ",
      tbiqol_pain_tscore ~ "Pain",
      tbiqol_posaffect_tscore ~ "Positive Effect",
      tbiqol_resilience_tscore ~ "Resilience",
      tbiqol_satissra_tscore ~ "Satisfaction SRA",
      tbiqol_selfesteem_tscore ~ "Self esteem",
      tbiqol_stigma_tscore ~ "Stigma",
      tbiqol_ue_tscore ~ "Upper Extremity",
      severity ~ "Severity of Injury"
    )
  ) %>%
  add_p(
    test = list(all_continuous() ~ "t.test", all_categorical() ~ "chisq.test"),
    pvalue_fun = ~style_pvalue(.x, digits = 2)
  ) %>%
  add_n()

print(tbiqol_table)
```



## TBI Composite
Comparison of composite scores for TBI QOL by severity of injury. Composite scores were calculated using: 

Tyner, C. E., Boulton, A. J., Sherer, M., Kisala, P. A., Glutting, J. J., & Tulsky, D. S. (2020). Development of Composite Scores for the TBI-QOL. Arch Phys Med Rehabil, 101(1), 43-53. https://doi.org/10.1016/j.apmr.2018.05.036 


```{r tbiqol compare, results='asis', echo=FALSE, include=TRUE}
tbiqol_composite_table <- df_demo %>%
  subset(., select = c(phys_health_index, emo_health_index, cog_health_index, soc_health_index, glob_health_index, severity)) %>%
  tbl_summary(
    missing = "no",
    by = severity,
    type = list(
      c(phys_health_index, emo_health_index, cog_health_index, soc_health_index, glob_health_index) ~ "continuous",
      c(severity) ~ "categorical"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)"),
    label = list(
      phys_health_index ~ "Physical Health Index",
      emo_health_index ~ "Emotional Health Index",
      cog_health_index ~ "Cognitive Health Index",
      soc_health_index ~ "Social Health Index",
      glob_health_index ~ "Global Health Index",
      severity ~ "Severity of Injury"
    )
  ) %>%
  add_p(
    test = list(all_continuous() ~ "t.test", all_categorical() ~ "chisq.test"),
    pvalue_fun = ~style_pvalue(.x, digits = 2)
  ) %>%
  add_n()

print(tbiqol_composite_table)   
```
```{r save table TBIQOL composite, echo=FALSE, include=FALSE}
#to save table to word doc
library(gt)
library(gtsummary)

gt_tbiqol_composite_table <- as_gt(tbiqol_composite_table)
   gtsave(gt_tbiqol_composite_table, filename = "tbiqol_composite.docx")
```

## Predictive variables 
Table 2 in dissertation

This table compares only the Personal and Environmental Protective factors and self-regulation outlined in the dissertation. Note that the Cognitive Health Composite score was not used as it includes executive functioning, which in this paper is considered a self-regulatory process. Therefore, general cognitive functioning was used which assesses memory and concentration.

```{r included variables compare, results='asis', echo=FALSE, include=TRUE}
PPF_table <- df_demo %>%
  subset(., select = c(phys_health_index, emo_health_index, tbiqol_genconcern_tscore, bfi_extraversion, bfi_agreeable, bfi_consciousness, bfi_neuroticism, bfi_openness, income, marital_status, spstotal, frsbe_exec, frsbe_disinhib, frsbe_apathy, frsbe_total, severity)) %>%
  tbl_summary(
    missing = "no",
    by = severity,
    type = list(
      c(phys_health_index, emo_health_index, tbiqol_genconcern_tscore, bfi_extraversion, bfi_agreeable, bfi_consciousness, bfi_neuroticism, bfi_openness) ~ "continuous",
      c(severity) ~ "categorical"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)"),
    label = list(
      phys_health_index ~ "Physical Health Index",
      emo_health_index ~ "Emotional Health Index",
      tbiqol_genconcern_tscore ~ "General Cognition",
      bfi_extraversion ~ "Extraversion", 
      bfi_agreeable ~ "Agreeable", 
      bfi_consciousness ~ "Consciousness", 
      bfi_neuroticism ~ "Neuroticism", 
      bfi_openness ~ "Openness",
      income ~ "Annual household income",
      marital_status ~ "Marital status",
      spstotal ~ "Social Support",
      frsbe_exec ~ "Executive function",
      frsbe_disinhib ~ "Disinhibition",
      frsbe_apathy ~ "Apathy",
      frsbe_total ~ "Total score",
      severity ~ "Severity of Injury"
    )
  ) %>%
  add_p(
    test = list(all_continuous() ~ "t.test", all_categorical() ~ "chisq.test"),
    pvalue_fun = ~style_pvalue(.x, digits = 2)
  ) %>%
  add_n()

print(PPF_table)   
```


```{r save tableTotal, echo=FALSE, include=FALSE}
#to save table to word doc
library(gt)
library(gtsummary)

gt_PPF_table <- as_gt(PPF_table)
   gtsave(gt_PPF_table, filename = "predictive_variables_table.docx")
```

Below is the t-test for SPS total, which was significantly different between severity of injury

```{r ttest sps, echo=FALSE, include=TRUE}

#significant difference in SPS between groups. t-test for t value

ttest_spstotal <- t.test(df_mod$spstotal, df_severe$spstotal)
print(ttest_spstotal)
```

# Descriptive Statistics
Descriptive statistics for each variable of interest for the data set including mean, median, SD, and IQR, kurtosis and se

```{r descriptive, echo=FALSE, include=TRUE, results='asis'}
summary_stats <- describeBy(df) %>% round(2)

# Display the summary statistics using kable
knitr::kable(summary_stats)
```




## ACS3

Outcome variable: ACS3 for all scores mean(sd)

```{r table ACS mean(sd), results='asis', echo=FALSE, include=TRUE}
mean_sd_acs <- df_demo %>%
  subset(., select = c(acsg_prev, acsg_curr, acsg_retain, acsi_prev, acsi_curr, acsi_retain, acsl_prev, acsl_curr, acsl_retain, acsf_prev, acsf_curr, acsf_retain, acss_prev, acss_curr, acss_retain)) %>%
  tbl_summary(
    missing = "no",
    type = list(
      c(acsg_prev, acsg_curr, acsg_retain, acsi_prev, acsi_curr, acsi_retain, acsl_prev, acsl_curr, acsl_retain, acsf_prev, acsf_curr, acsf_retain, acss_prev, acss_curr, acss_retain) ~ "continuous"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    label = list(
      acsg_prev ~ "ACS Global Before",
      acsg_curr ~ "ACS Global Current",
      acsg_retain ~ "Global Retained (%)",
      acsi_prev ~ "ACS IADL Before",
      acsi_curr ~ "ACS IADL Current",
      acsi_retain ~ "IADL Retained (%)",
      acsl_prev ~ "ACS Leisure Before",
      acsl_curr ~ "ACS Leisure Current",
      acsl_retain ~ "Leisure Retained (%)",
      acsf_prev ~ "ACS Fitness Before",
      acsf_curr ~ "ACS Fitness Current",
      acsf_retain ~ "Fitness Retained (%)",
      acss_prev ~ "ACS Social Before",
      acss_curr ~ "ACS Social Current",
      acss_retain ~ "Social Retained (%)"
    )
  ) 


print(mean_sd_acs)   
```

# Correlations

## All variables
Correlation of all variables of interest with TBI QOL subscores. While too small to read in HTML print out, nice reference during analysis

```{r all variables, fig.width=15,fig.height=15, results='asis', echo=FALSE, include=TRUE}
library(ggplot2)
library(reshape2)
library(Hmisc)

all_variables <- c("age_current", "time_injury", "gender", "edu", "work_current", "income", "severity", "substance", "acsg_prev", "acsg_curr", "acsg_retain", "acsi_prev", "acsi_curr", "acsi_retain", "acsl_prev", "acsl_curr", "acsl_retain", "acsf_prev", "acsf_curr", "acsf_retain", "acss_prev", "acss_curr", "acss_retain","tbiqol_part_sra_tscore", "tbiqol_anxiety_tscore", "tbiqol_comm_tscore", "tbiqol_ue_tscore","tbiqol_depression_tscore", "tbiqol_fatigue_tscore", "tbiqol_genconcern_tscore", "tbiqol_grief_tscore", "tbiqol_mobility_tscore", "tbiqol_headache_tscore", "tbiqol_pain_tscore", "tbiqol_resilience_tscore", "tbiqol_satissra_tscore", "tbiqol_selfesteem_tscore", "tbiqol_stigma_tscore", "spstotal", "bfi_extraversion", "bfi_agreeable", "bfi_consciousness", "bfi_neuroticism", "bfi_openness", "frsbe_apathy", "frsbe_exec", "frsbe_disinhib", "frsbe_total")

all_variables <- intersect(all_variables, colnames(df))  # Ensure selected variables are in the dataframe

all_variables_df <- df[, all_variables]

cor_matrix <- rcorr(as.matrix(all_variables_df),type = "spearman")$r
cor_matrix[upper.tri(cor_matrix)] <- NA
p_matrix <- rcorr(as.matrix(all_variables_df),type = "spearman")$P
p_matrix[is.na(p_matrix)]=.0000001
p_matrix[upper.tri(p_matrix)] <- NA

# Melt the correlation matrix for ggplot
melted_cor <- melt(cor_matrix,na.rm = T)
melted_p = melt(p_matrix,na.rm = T)

melted_cor$p=melted_p$value
melted_cor$psig=""
melted_cor$psig[melted_cor$p<.05]="*"
melted_cor$psig[melted_cor$p<.01]="**"
melted_cor$psig[melted_cor$p<.001]="***"

# Create a heatmap using ggplot2
ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), vjust = 1, size = 2) +
  geom_text(aes(label = psig), vjust = .25,size=5) +
  scale_fill_gradient2(low = "purple", mid = "white", high = "orange", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, hjust = 1))+
  labs(caption = "<.05 = *, <.01 = **, <.001 = ***")+
  xlab("")+
  ylab("")+
  ggtitle("Correlation Matrix all variables")

```


```{r rename variables, results='asis', echo=FALSE, include=FALSE}
#Rename Variables in new dataset
df2 <- read_excel('/Users/amandagahlot/Documents/Dissertation/R_Output/cleaned_data_Final.xlsx')

# Rename multiple variables
df2 <- df2 %>%
  rename(Global = acsg_retain,
         IADL = acsi_retain,
         Leisure = acsl_retain,
         Fitness = acsf_retain,
         Social = acss_retain,
         Age = age_current,
         TimeSinceInjury = time_injury,
         Extraversion = bfi_extraversion,
         Agreeable = bfi_agreeable,
         Consciousness =bfi_consciousness,
         Neuroticism = bfi_neuroticism,
         Openness = bfi_openness,
         Apathy = frsbe_apathy,
         ExecFunc = frsbe_exec,
         Disinhibition = frsbe_disinhib,
         Total = frsbe_total,
         SocialSupport = spstotal,
         Communication = tbiqol_comm_tscore,
         ExecFuncQOL = tbiqol_execfunc_tscore, 
         GeneralCognition = tbiqol_genconcern_tscore,
         UpperExtremity = tbiqol_ue_tscore, 
         Fatigue = tbiqol_fatigue_tscore, 
         Mobility = tbiqol_mobility_tscore, 
         Headache = tbiqol_headache_tscore,
         Pain = tbiqol_pain_tscore,
         Anger = tbiqol_anger_tscore,
         PositiveAffect = tbiqol_posaffect_tscore,
         Age = age_current,
         Education = edu,
         Work = work_current,
         SubstanceUse = substance,
         Anxiety = tbiqol_anxiety_tscore, 
         Depression = tbiqol_depression_tscore, 
         Grief = tbiqol_grief_tscore, 
         TraitResilience = tbiqol_resilience_tscore,  
         SelfEsteem = tbiqol_selfesteem_tscore, 
         Stigma = tbiqol_stigma_tscore,
         TimeSinceInjury = time_injury,
         MaritalStatus = marital_status,
         SocialSupport = spstotal,
         HouseholdSize = house_size,
         PhysicalHealth = phys_health_index,
         EmotionalHealth = emo_health_index)
         

         

```

Correlation matrix of PPF only (using composite TBIQOL Scores)

```{r ppf corr, fig.width=15,fig.height=15, echo=FALSE, include=TRUE}
library(ggplot2)
library(reshape2)
library(Hmisc)

PPF_variables <- c("Global", "IADL", "Leisure", "Fitness", "Social", "PhysicalHealth", "EmotionalHealth", "GeneralCognition", "Extraversion", "Agreeable", "Consciousness", "Neuroticism", "Openness")

PPF_variables <- intersect(PPF_variables, colnames(df2))  # Ensure selected variables are in the dataframe

PPF_variables_df2 <- df2[, PPF_variables]

cor_matrix <- rcorr(as.matrix(PPF_variables_df2),type = "spearman")$r
cor_matrix[upper.tri(cor_matrix)] <- NA
p_matrix <- rcorr(as.matrix(PPF_variables_df2),type = "spearman")$P
p_matrix[is.na(p_matrix)]=.0000001
p_matrix[upper.tri(p_matrix)] <- NA

# Melt the correlation matrix for ggplot
melted_cor <- melt(cor_matrix,na.rm = T)
melted_p = melt(p_matrix,na.rm = T)

melted_cor$p=melted_p$value
melted_cor$psig=""
melted_cor$psig[melted_cor$p<.05]="*"
melted_cor$psig[melted_cor$p<.01]="**"
melted_cor$psig[melted_cor$p<.001]="***"

# Create a heatmap using ggplot2
ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value,2)), vjust = 1) +
  geom_text(aes(label = psig), vjust = .25,size=5) +
  scale_fill_gradient2(low = "purple", mid = "white", high = "orange", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, hjust = 1))+
  labs(caption = "<.05 = *, <.01 = **, <.001 = ***")+
  xlab("")+
  ylab("")+
  ggtitle("Correlation Matrix Personal Protective Factors")


```



## Included Variables

Matrix with heat map for all included variables in dissertation. Figure 4 in dissertation

```{r ppf_only corr, fig.width=15,fig.height=15, echo=FALSE, include=TRUE}
library(ggplot2)
library(reshape2)
library(Hmisc)

# Define QOL_PPF_variables
QOL_PPF_variables <- c("Global", "IADL", "Leisure", "Fitness", "Social", "PhysicalHealth", "GeneralCognition", "EmotionalHealth", "Extraversion", "Agreeable", "Consciousness", "Neuroticism", "Openness", "income", "MaritalStatus", "SocialSupport", "Apathy", "Disinhibition", "ExecFunc", "Total")

# Ensure selected variables are in the dataframe
QOL_PPF_variables <- intersect(QOL_PPF_variables, colnames(df2))

# Extract relevant data
QOL_PPF_df2 <- df2[, QOL_PPF_variables]

# Calculate correlation matrix
cor_matrix <- rcorr(as.matrix(QOL_PPF_df2), type = "spearman")$r
cor_matrix[upper.tri(cor_matrix)] <- NA
p_matrix <- rcorr(as.matrix(QOL_PPF_df2), type = "spearman")$P
p_matrix[is.na(p_matrix)] <- .0000001
p_matrix[upper.tri(p_matrix)] <- NA

# Melt the correlation matrix for ggplot
melted_cor <- melt(cor_matrix, na.rm = TRUE)
melted_p <- melt(p_matrix, na.rm = TRUE)

melted_cor$p <- melted_p$value
melted_cor$psig <- ""
melted_cor$psig[melted_cor$p < .05] <- "*"
melted_cor$psig[melted_cor$p < .01] <- "**"
melted_cor$psig[melted_cor$p < .001] <- "***"

# Create a heatmap using ggplot2
ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), vjust = 1, size=5, family = "Times New Roman") +
  geom_text(aes(label = psig), vjust = .25, size = 5, family = "Times New Roman") +
  scale_fill_gradient2(low = "purple", mid = "white", high = "orange", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab",
                       name = "Correlation") +
  theme_minimal(base_family = "Times New Roman") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
        axis.text.y = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
        legend.position = "bottom",
        legend.justification = "right",
        legend.box = "horizontal") +
  labs(caption = "<.05 = *, <.01 = **, <.001 = ***",
       x = "",
       y = "") +
  ggtitle("Correlation Matrix Personal Protective Factors with ACS Variables") +
  guides(fill = guide_colorbar(title.position = "right"))

```


Below is the breakdown of all TBIQOL sub scores with the ACS3. While not included in this study, 
helpful for discussion and future publications.

```{r subscale corr, fig.width=15,fig.height=15, echo=FALSE, include=TRUE}

# Define QOL_variables
QOL_variables <- c("Global", "IADL", "Leisure", "Fitness", "Social", "Anxiety", "Depression", "Grief", "Resilience", "SelfEsteem", "Stigma", "Communication", "GeneralCognition", "ExecFuncQOL", "UpperExtremity", "Fatigue", "Mobility", "Headache", "Pain")

# Ensure selected variables are in the dataframe
QOL_variables <- intersect(QOL_variables, colnames(df2))

# Extract relevant data
QOL_df2 <- df2[, QOL_variables]

# Calculate correlation matrix
cor_matrix <- rcorr(as.matrix(QOL_df2), type = "spearman")$r
cor_matrix[upper.tri(cor_matrix)] <- NA
p_matrix <- rcorr(as.matrix(QOL_df2), type = "spearman")$P
p_matrix[is.na(p_matrix)] <- .0000001
p_matrix[upper.tri(p_matrix)] <- NA

# Melt the correlation matrix for ggplot
melted_cor <- melt(cor_matrix, na.rm = TRUE)
melted_p <- melt(p_matrix, na.rm = TRUE)

melted_cor$p <- melted_p$value
melted_cor$psig <- ""
melted_cor$psig[melted_cor$p < .05] <- "*"
melted_cor$psig[melted_cor$p < .01] <- "**"
melted_cor$psig[melted_cor$p < .001] <- "***"

# Create a heatmap using ggplot2
ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value,2)), vjust = 1) +
  geom_text(aes(label = psig), vjust = .25,size=5) +
  scale_fill_gradient2(low = "purple", mid = "white", high = "orange", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, hjust = 1))+
  labs(caption = "<.05 = *, <.01 = **, <.001 = ***")+
  xlab("")+
  ylab("")+
  ggtitle("Correlation Matrix Personal Protective Factors with ACS Variables") +
  guides(fill = guide_colorbar(title.position = "right"))

```






## FrSBe and TBI-QOL

TBI QOL subscales with the FrSBe


```{r qol and frsbe corr, fig.width=10,fig.height=8, echo=FALSE, include=TRUE}

QOL_FRSBE_variables <- c("frsbe_apathy", "frsbe_disinhib", "frsbe_exec", "frsbe_total", "tbiqol_part_sra_tscore", "tbiqol_anxiety_tscore", "tbiqol_comm_tscore","tbiqol_ue_tscore","tbiqol_depression_tscore", "tbiqol_dyscontrol_tscoree", "tbiqol_execfunc_tscore", "tbiqol_fatigue_tscore", "tbiqol_genconcern_tscore", "tbiqol_grief_tscore", "tbiqol_mobility_tscore", "tbiqol_headache_tscore", "tbiqol_pain_tscore", "tbiqol_resilience_tscore", "tbiqol_satissra_tscore", "tbiqol_selfesteem_tscore", "tbiqol_stigma_tscore")

QOL_FRSBE_variables <- intersect(QOL_FRSBE_variables, colnames(df))  # Ensure selected variables are in the dataframe

QOL_FRSBE_df <- df[, QOL_FRSBE_variables]

cor_matrix <- rcorr(as.matrix(QOL_FRSBE_df ),type = "spearman")$r
cor_matrix[upper.tri(cor_matrix)] <- NA
p_matrix <- rcorr(as.matrix(QOL_FRSBE_df ),type = "spearman")$P
p_matrix[is.na(p_matrix)]=.0000001
p_matrix[upper.tri(p_matrix)] <- NA

# Melt the correlation matrix for ggplot
melted_cor <- melt(cor_matrix,na.rm = T)
melted_p = melt(p_matrix,na.rm = T)

melted_cor$p=melted_p$value
melted_cor$psig=""
melted_cor$psig[melted_cor$p<.05]="*"
melted_cor$psig[melted_cor$p<.01]="**"
melted_cor$psig[melted_cor$p<.001]="***"

# Create a heatmap using ggplot2
ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value,2)), vjust = 1) +
  geom_text(aes(label = psig), vjust = .25,size=5) +
  scale_fill_gradient2(low = "purple", mid = "white", high = "orange", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, hjust = 1))+
  labs(caption = "<.05 = *, <.01 = **, <.001 = ***")+
  xlab("")+
  ylab("")+
  ggtitle("Correlation Matrix TBI-QOL Subscale and FrSBe Variables")
```



# RQ1: Regression Analysis

Research Question 1
1.	What is the relationship between protective factors and self-regulation with resiliency-related outcomes such as re-engagement in meaningful activities?
a.	To what extent do protective factors and self-regulation predict resiliency-related outcomes in the TBI population?
Hypothesis: Higher self-regulation will be associated with better resiliency-related outcomes
b.	To what extent does self-regulation mediate or moderate the influence of protective factors on resiliency-related outcomes after TBI?
Hypothesis: Self-regulation will impact the relationship between protective factors and resiliency-related outcomes

## RQ1a
First, we'll look at the hierarchical linear model as outlined in Chapter 3. Then, to dive deeper, a "post hoc" analysis of each subscale of the ACS and use AIC to determine model of best fit. 

## ACS Global
In this section, we'll do the original hierarchical model with protective and environmental protective factors in the first step and then total self-regulation score added for the second.
*note that the cognitive composite score is not included as it includes exec functioning, which in this paper is seen as a self-regulatory process. therefore, gen concerns (memory and concentration) is used as cognitive protective factor

```{r step 1, echo=TRUE, include=TRUE}
step1 <- lm(acsg_retain~age_current, data=df)
summary(step1)
```

```{r step 2, echo=TRUE, include=TRUE}
step2<- lm(acsg_retain~age_current+phys_health_index+tbiqol_genconcern_tscore+emo_health_index+ spstotal, data=df)
summary(step2)
```

```{r nested model 12 comparison, echo=TRUE, include=TRUE}
#Nested Model Comparison
anova(step1, step2)
```

```{r change in r-squared 12, echo=TRUE, include=TRUE}
#change in R-squared
summary(step2)$r.squared - summary(step1)$r.squared
```

```{r step 3, echo=TRUE, include=TRUE}
step3<- lm(acsg_retain~age_current+phys_health_index+tbiqol_genconcern_tscore+emo_health_index+ spstotal+frsbe_total, data=df)
summary(step3)
```

```{r nested model 23 comparison, echo=TRUE, include=TRUE}
#Nested Model Comparison
anova(step2, step3)
```

```{r change in r-squared 23, echo=TRUE, include=TRUE}
#change in R-squared
summary(step3)$r.squared - summary(step2)$r.squared
```


### Assumptions tested
Test for multicollinearity

```{r VIF, include=TRUE, echo=FALSE}
library(car)
vif(step3)
```


## Post Hoc AIC Models

As we have a smaller n and need to be parsimonious with the variables we use in the regression model, we'll look at several models based on correlations (higher correlations added to the models) and then calculate the AIC. The lower AIC, the better the fit and that model will be used

Note that all assumptions were tested for each model and were met



### ACS3 Social

```{r summary models AIC acss, echo=FALSE, include=TRUE}
library(AICcmodavg)
#composite scores
model1 <- lm(acss_retain~phys_health_index+cog_health_index+emo_health_index+spstotal, data=df)

model2 <- lm(acss_retain~phys_health_index+cog_health_index+emo_health_index+spstotal+frsbe_total, data=df)

model3 <- lm(acss_retain~phys_health_index+cog_health_index+emo_health_index+spstotal+frsbe_apathy, data=df)

#individual
model4 <- lm(acss_retain~tbiqol_fatigue_tscore+tbiqol_genconcern_tscore+tbiqol_depression_tscore+tbiqol_anxiety_tscore+spstotal+spstotal, data=df)
model5 <- lm(acss_retain~tbiqol_fatigue_tscore+tbiqol_genconcern_tscore+tbiqol_depression_tscore+tbiqol_anxiety_tscore+spstotal+frsbe_total, data=df)
model6 <- lm(acss_retain~tbiqol_fatigue_tscore+tbiqol_genconcern_tscore+tbiqol_depression_tscore+tbiqol_anxiety_tscore+spstotal+frsbe_apathy, data=df)
model7 <- lm(acss_retain~tbiqol_fatigue_tscore+tbiqol_genconcern_tscore+tbiqol_depression_tscore+tbiqol_anxiety_tscore+frsbe_apathy, data=df)
model8 <- lm(acss_retain~tbiqol_fatigue_tscore+tbiqol_genconcern_tscore+tbiqol_depression_tscore+tbiqol_anxiety_tscore+frsbe_total, data=df) 
model9 <- lm(acss_retain~tbiqol_fatigue_tscore+tbiqol_comm_tscore+tbiqol_depression_tscore+tbiqol_anxiety_tscore+frsbe_total, data=df)
model10 <- lm(acss_retain~tbiqol_fatigue_tscore+tbiqol_comm_tscore+tbiqol_depression_tscore+tbiqol_anxiety_tscore+frsbe_total, data=df)
model11 <- lm(acss_retain~tbiqol_fatigue_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+ tbiqol_depression_tscore+tbiqol_anxiety_tscore+frsbe_apathy, data=df)

models <- list (model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11)

mod.names <- c('model1', 'model2', 'model3', 'model4', 'model5','model6', 'model7', 'model8', 'model9', 'model10', 'model11')

aictab(cand.set = models, modnames = mod.names)
```

```{r summary model selected acss, echo=FALSE, include=TRUE}
summary(model7)
```
### ACS3 IADL

```{r summary of models AIC acgi, include=TRUE, echo=FALSE}
library(AICcmodavg)
#composite scores
model1 <- lm(acsi_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+tbiqol_grief_tscore+spstotal+frsbe_total, data=df)
model2 <- lm(acsi_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+tbiqol_grief_tscore+spstotal+frsbe_apathy, data=df)
model3<- lm(acsi_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+tbiqol_grief_tscore+spstotal+frsbe_exec, data=df)
model4 <- lm(acsi_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+spstotal+tbiqol_ue_tscore+frsbe_apathy, data=df)
model5 <- lm(acsi_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+tbiqol_ue_tscore+spstotal+frsbe_apathy, data=df)
model6<- lm(acsi_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+tbiqol_ue_tscore+frsbe_apathy, data=df)

models <- list (model1, model2, model3, model4, model5, model6)

mod.names <- c('model1', 'model2', 'model3', 'model4', 'model5','model6')

aictab(cand.set = models, modnames = mod.names)
```



```{r model included acsi, echo=FALSE, include=FALSE}
summary(model6)
```


### ACS3 Leisure

```{r leisure acs AIC, echo=FALSE, include=TRUE}
model1 <- lm (acsl_retain~tbiqol_mobility_tscore+tbiqol_ue_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+frsbe_total, data=df)
model2 <- lm (acsl_retain~tbiqol_mobility_tscore+tbiqol_ue_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+tbiqol_grief_tscore+frsbe_total, data=df)
model3 <-lm (acsl_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+frsbe_total, data=df)
model4 <-lm (acsl_retain~tbiqol_mobility_tscore+tbiqol_grief_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+frsbe_total, data=df)
model5 <-lm (acsl_retain~tbiqol_ue_tscore+tbiqol_grief_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+frsbe_total, data=df)
model6 <-lm (acsl_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+frsbe_apathy, data=df)
model7 <-lm (acsl_retain~tbiqol_mobility_tscore+tbiqol_genconcern_tscore+tbiqol_comm_tscore+frsbe_exec, data=df)

models <- list (model1, model2, model3, model4, model5, model6, model7)

mod.names <- c('model1', 'model2', 'model3', 'model4', 'model5', 'model6', 'model7')

aictab(cand.set = models, modnames = mod.names)
```

```{r summary selected model acsl, echo=FALSE, include=TRUE}
summary(model6)
```

### ACS3 Fitness

```{r fitness AIC, echo=FALSE, include=TRUE}
model1 <- lm (acsf_retain~tbiqol_mobility_tscore+tbiqol_pain_tscore+tbiqol_genconcern_tscore+tbiqol_anxiety_tscore+tbiqol_stigma_tscore+frsbe_total, data=df)
model2 <- lm (acsf_retain~phys_health_index+tbiqol_genconcern_tscore+tbiqol_anxiety_tscore+tbiqol_stigma_tscore, data=df)
model3 <-lm (acsf_retain~tbiqol_mobility_tscore+tbiqol_pain_tscore+tbiqol_genconcern_tscore+tbiqol_anxiety_tscore+tbiqol_grief_tscore, data=df)
model4 <-lm (acsf_retain~phys_health_index+tbiqol_genconcern_tscore+tbiqol_anxiety_tscore+tbiqol_grief_tscore, data=df)
model5 <- lm (acsf_retain~tbiqol_mobility_tscore+tbiqol_pain_tscore+tbiqol_genconcern_tscore+tbiqol_anxiety_tscore+tbiqol_grief_tscore+tbiqol_stigma_tscore, data=df)
model6 <- lm (acsf_retain~tbiqol_mobility_tscore+tbiqol_pain_tscore+tbiqol_genconcern_tscore+tbiqol_anxiety_tscore+tbiqol_stigma_tscore+frsbe_total+income, data=df)
model7 <- lm (acsf_retain~phys_health_index+tbiqol_genconcern_tscore+tbiqol_anxiety_tscore+tbiqol_stigma_tscore+frsbe_total+income, data=df)
model8 <- lm (acsf_retain~phys_health_index+tbiqol_genconcern_tscore+tbiqol_anxiety_tscore+tbiqol_stigma_tscore+income, data=df)

models <- list (model1, model2, model3, model4, model5, model6, model7, model8)

mod.names <- c('model1', 'model2', 'model3', 'model4', 'model5', 'model6', 'model7', 'model8')

aictab(cand.set = models, modnames = mod.names)
```

```{r selected model fitness, echo=FALSE, include=TRUE}
summary(model8)
```
## RQ1b
### Moderation 
For moderation, looking at personal protective factors and environmental protective factors from original model
```{r moderation mobility, include=TRUE, echo=FALSE}
mod_acsg_phys <- lm(acsg_retain~phys_health_index*frsbe_total, data=df)
summary(mod_acsg_phys)
```
```{r moderation gen concern, include=TRUE, echo=FALSE}
mod_acsg_genconcern <- lm(acsg_retain~tbiqol_genconcern_tscore*frsbe_total, data=df)
summary(mod_acsg_genconcern)
```

```{r moderation emo, include=TRUE, echo=FALSE}
mod_acsg_emo <- lm(acsg_retain~emo_health_index*frsbe_total, data=df)
summary(mod_acsg_emo)
```

```{r moderation SPS, include=TRUE, echo=FALSE}
mod_acsg_sps <- lm(acsg_retain~spstotal*frsbe_total, data=df)
summary(mod_acsg_sps)
```
There was no moderating effect of apathy on any of the predictors. 

### Mediation

Here we look at mediation effect of the total FrSBe scores on the personal and environmental factors used in the post hoc model (mobility, general cog functioning, anxiety, depression, and social support)

How to read: 
ACME = indirect effect
ADE = direct effect
ACME + ADE = total effect


```{r load library mediation, echo=FALSE, include=FALSE}
library(mediation)
library(JSmediation)
```
#### Physical Health


```{r mediation phys health}
# Initial Model
model1 <- lm(acsg_retain ~ phys_health_index, df) # Y ~ X, DV predicted by IV - no mediation considered - total effect
summary(model1)

# Mediation paths
medmodel1 <- lm(frsbe_total ~ phys_health_index, df) # M ~ X, mediator predicted by X
outputmodel1 <- lm(acsg_retain ~ phys_health_index + frsbe_total, df) # Y ~ X + M, DV predicted by mediator, adjusting for IV

summary(medmodel1)
summary(outputmodel1)


# Mediation test
mediation <- mediate(medmodel1, # Mediator model
                    outputmodel1, # Outcome model
                    boot = T, # Ask for bootstrapped confidence intervals
                    treat="phys_health_index", # Name of the x variable
                    mediator="frsbe_total" # Name of the m variable
                    )
# if you don't want bootstrap, just delete 'sims' line and set boot = F

summary(mediation)
plot(mediation)

```
There is a significant indirect effect and an insignificant direct effect, indicating total mediation

```{r path mediation phys, echo=FALSE, include=TRUE}
library(diagram)

patha <- paste(round(as.numeric(coef(medmodel1)[2]),2))
patha
pathb <- paste(round(as.numeric(coef(outputmodel1)[3]),2))
pathb

# indirect
direct <- paste(round(mediation$z.avg,2)) # direct
total <- paste(round((mediation$d.avg + mediation$z.avg),2)) # total

pathc <- paste(direct,"(",total,")")

data <- c(0, patha, 0,
          0, 0, 0, 
          pathb, pathc, 0) # order: top = effect of IV on mediator; bottom left = effect of mediator on DV; bottom middle = direct effect (total effect)
M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
plot<- plotmat (M, pos=c(1,2), 
                name= c("Self-regulation: Total","Physical Health", "ACS Global"), # order: Mediator, IV, DV 
                box.type = "rect", box.size = 0.12, box.prop=0.5,  curve=0)

```
#### Cognitive Health

```{r cog health index, echo=FALSE, include=TRUE}
# MEDIATION
# Initial Model
model2 <- lm(acsg_retain ~ tbiqol_genconcern_tscore, df) # Y ~ X, DV predicted by IV - no mediation considered - total effect
summary(model2)

# Mediation paths
medmodel2 <- lm(frsbe_total ~ tbiqol_genconcern_tscore, df) # M ~ X, mediator predicted by X
outputmodel2 <- lm(acsg_retain ~ tbiqol_genconcern_tscore + frsbe_total, df) # Y ~ X + M, DV predicted by mediator, adjusting for IV

summary(medmodel2)
summary(outputmodel2)


# Mediation test
mediation <- mediate(medmodel2, # Mediator model
                    outputmodel2, # Outcome model
                    boot = T, # Ask for bootstrapped confidence intervals
                    treat="tbiqol_genconcern_tscore", # Name of the x variable
                    mediator="frsbe_total" # Name of the m variable
                    )
# if you don't want bootstrap, just delete 'sims' line and set boot = F

summary(mediation)
plot(mediation)
```
There is no significant indirect effect. No mediation

#### Emotional Health


```{r mediation emo health, echo=FALSE, include=TRUE}
# Initial Model
model1 <- lm(acsg_retain ~ emo_health_index, df) # Y ~ X, DV predicted by IV - no mediation considered - total effect
summary(model1)

# Mediation paths
medmodel1 <- lm(frsbe_total ~ emo_health_index, df) # M ~ X, mediator predicted by X
outputmodel1 <- lm(acsg_retain ~ emo_health_index + frsbe_total, df) # Y ~ X + M, DV predicted by mediator, adjusting for IV

summary(medmodel1)
summary(outputmodel1)


# Mediation test
mediation <- mediate(medmodel1, # Mediator model
                    outputmodel1, # Outcome model
                    boot = T, # Ask for bootstrapped confidence intervals
                    treat="emo_health_index", # Name of the x variable
                    mediator="frsbe_total" # Name of the m variable
                    )
# if you don't want bootstrap, just delete 'sims' line and set boot = F

summary(mediation)
plot(mediation)

```
There is no significant indirect effect indicating no mediation 
```{r path mediation emo, echo=FALSE, include=TRUE}

patha <- paste(round(as.numeric(coef(medmodel1)[2]),2))
patha
pathb <- paste(round(as.numeric(coef(outputmodel1)[3]),2))
pathb

# indirect
direct <- paste(round(mediation$z.avg,2)) # direct
total <- paste(round((mediation$d.avg + mediation$z.avg),2)) # total

pathc <- paste(direct,"(",total,")")

data <- c(0, patha, 0,
          0, 0, 0, 
          pathb, pathc, 0) # order: top = effect of IV on mediator; bottom left = effect of mediator on DV; bottom middle = direct effect (total effect)
M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
plot<- plotmat (M, pos=c(1,2), 
                name= c("Self-regulation: Total","Emotional Health", "ACS Global"), # order: Mediator, IV, DV 
                box.type = "rect", box.size = 0.12, box.prop=0.5,  curve=0)

```
#### SPS


```{r mediation social support, echo=FALSE, include=TRUE}
# Initial Model
model1 <- lm(acsg_retain ~ spstotal, df) # Y ~ X, DV predicted by IV - no mediation considered - total effect
summary(model1)

# Mediation paths
medmodel1 <- lm(frsbe_total ~ spstotal, df) # M ~ X, mediator predicted by X
outputmodel1 <- lm(acsg_retain ~ spstotal + frsbe_total, df) # Y ~ X + M, DV predicted by mediator, adjusting for IV

summary(medmodel1)
summary(outputmodel1)


# Mediation test
mediation <- mediate(medmodel1, # Mediator model
                    outputmodel1, # Outcome model
                    boot = T, # Ask for bootstrapped confidence intervals
                    treat="spstotal", # Name of the x variable
                    mediator="frsbe_total" # Name of the m variable
                    )
# if you don't want bootstrap, just delete 'sims' line and set boot = F

summary(mediation)
plot(mediation)

```
There is a significant indirect effect and insignificant direct effect indicating full mediation 

```{r path mediation social, echo=FALSE, include=TRUE}

patha <- paste(round(as.numeric(coef(medmodel1)[2]),2))
patha
pathb <- paste(round(as.numeric(coef(outputmodel1)[3]),2))
pathb

# indirect
direct <- paste(round(mediation$z.avg,2)) # direct
total <- paste(round((mediation$d.avg + mediation$z.avg),2)) # total

pathc <- paste(direct,"(",total,")")

data <- c(0, patha, 0,
          0, 0, 0, 
          pathb, pathc, 0) # order: top = effect of IV on mediator; bottom left = effect of mediator on DV; bottom middle = direct effect (total effect)
M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
plot<- plotmat (M, pos=c(1,2), 
                name= c("Self-regulation: Total","Social support", "ACS Global"), # order: Mediator, IV, DV 
                box.type = "rect", box.size = 0.12, box.prop=0.5,  curve=0)
```

# RQ2: Time Since Injury
2.	How does time since injury influence resiliency?
a.	Is time after injury associated with an individual’s ability to re-engage in meaningful activities?
b.	To what extent do the relationships between protective factors and self-regulatory processes with resiliency-related outcomes change with time since sustaining TBI?
Hypothesis: Time since injury will be associated with resiliency, leading to different resiliency-related outcomes

To answer these questions, first look at descriptive statistics, then regression model with time since injury included, lastly, investigate what, if any, role time since injury has on protective factors and self-regulation

## Descriptives

```{r summary time since injury, echo=FALSE, include=TRUE}
selected_vars_acs <- c("time_injury")

summary_table <- do.call(rbind, lapply(df[selected_vars_acs], function(x) round(summary(x), 2)))

print(summary_table)
```


## Correlation ACS

```{r corr time since injury with acsg, fig.width=15,fig.height=15, echo=FALSE, include=TRUE}
# Define variables
timesinceinjury_variables <- c("TimeSinceInjury", "Global", "IADL", "Leisure", "Fitness", "Social", "acsg_before", "acsg_after", "acsi_before", "acsi_after","acsl_before", "acsl_after","acsf_before", "acsf_after","acss_before", "acss_after")

# Ensure selected variables are in the dataframe
timesinceinjury_variables <- intersect(timesinceinjury_variables, colnames(df2))

# Extract relevant data
timesinceinjury_df2 <- df2[, timesinceinjury_variables]

# Calculate correlation matrix
cor_matrix <- rcorr(as.matrix(timesinceinjury_df2), type = "spearman")$r
cor_matrix[upper.tri(cor_matrix)] <- NA
p_matrix <- rcorr(as.matrix(timesinceinjury_df2), type = "spearman")$P
p_matrix[is.na(p_matrix)] <- .0000001
p_matrix[upper.tri(p_matrix)] <- NA

# Melt the correlation matrix for ggplot
melted_cor <- melt(cor_matrix, na.rm = TRUE)
melted_p <- melt(p_matrix, na.rm = TRUE)

melted_cor$p <- melted_p$value
melted_cor$psig <- ""
melted_cor$psig[melted_cor$p < .05] <- "*"
melted_cor$psig[melted_cor$p < .01] <- "**"
melted_cor$psig[melted_cor$p < .001] <- "***"

# Create a heatmap using ggplot2
ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), vjust = 1, family = "Times New Roman") +
  geom_text(aes(label = psig), vjust = 0.25, size = 5, family = "Times New Roman") +
  scale_fill_gradient2(low = "purple", mid = "white", high = "orange", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab",
                       name = "Correlation") +
  theme_minimal(base_family = "Times New Roman") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
        axis.text.y = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
        legend.position = "bottom",
        legend.justification = "right",
        legend.box = "horizontal") +
  labs(caption = "<.05 = *, <.01 = **, <.001 = ***",
       x = "",
       y = "") +
  ggtitle("Correlation Matrix Personal Protective Factors with ACS Variables") +
  guides(fill = guide_colorbar(title.position = "right"))

```

## Regression Analysis

### Global ACS
First, looking just at the relationship between time since injury and re-engagement while controlling for age.

```{r regression time since injury, echo=FALSE, include=TRUE}
model_timeinjury <- lm(acsg_retain~age_current+time_injury, data=df)
summary(model_timeinjury)
```
Controlling for age, there is no significant relationship between time since injury and re-engagement

### Social ACS3

```{r regression time since injury social, echo=FALSE, include=TRUE}
model_timeinjury_soc <- lm(acss_retain~age_current+time_injury, data=df)
summary(model_timeinjury_soc)
```

### IADL ACS3

```{r regression time since injury IADL, echo=FALSE, include=TRUE}
model_timeinjury_iadl <- lm(acsi_retain~age_current+time_injury, data=df)
summary(model_timeinjury_iadl)
```

### Leisure ACS3

```{r regression time since injury leisure, echo=FALSE, include=TRUE}
model_timeinjury_leisure <- lm(acsl_retain~age_current+time_injury, data=df)
summary(model_timeinjury_leisure)
```

### Fitness ACS3

```{r regression time since injury fitness, echo=FALSE, include=TRUE}
model_timeinjury_fitness <- lm(acsf_retain~age_current+time_injury, data=df)
summary(model_timeinjury_fitness)
```

## Hierarchical Regression: Step 4
```{r step 4, echo=FALSE, include=TRUE}
step4<- lm(acsg_retain~age_current+phys_health_index+tbiqol_genconcern_tscore+emo_health_index+ spstotal+frsbe_total+time_injury, data=df)
summary(step4)
```


```{r nested model 34 comparison, echo=TRUE, include=TRUE}
#Nested Model Comparison
anova(step3, step4)
```

```{r change in r-squared 34, echo=TRUE, include=TRUE}
#change in R-squared
summary(step4)$r.squared - summary(step3)$r.squared
```


## POST HOC: Groups

Because there was no significant relationship between time since injury and outcomes BUT it was a significant predictor in the model, I seperated time since recovery into three groups to examine relationships further. 
Early = 6mo-3years
Mid = 3 to 10 years
Later = >10 years

1= everything <=3 and 3 is everything >=10
```{r creating new groups, echo=FALSE, include=FALSE}
df_time3 <- read_excel('/Users/amandagahlot/Documents/Dissertation/R_Output/cleaned_data_Final.xlsx')
df_time3$time_injury_ex <- ifelse(df_time3$time_injury <= 3, 'Early',
                           ifelse(df_time3$time_injury < 10, 'Mid', 'Later'))

```

```{r convert, echo=FALSE, include=FALSE}
# Convert df_time3$time_injury_ex to a factor
df_time3$time_injury_ex <- factor(df_time3$time_injury_ex, levels = c("Early", "Mid", "Later"))

# Convert the factor to numeric
df_time3$time_injury_ex_numeric <- as.numeric(df_time3$time_injury_ex)

```

```{r export for python, echo=FALSE, include=FALSE}
# Install and load the openxlsx package
library(openxlsx)

# Assuming df is your data frame
write.xlsx(df_time3, file = "time_injury.xlsx", rowNames = FALSE)
```


```{r demo 3 groups, results='asis', echo=FALSE, include=TRUE}
demo_table_time <- df_time3 %>%
  subset(., select = c(time_injury_ex, age_current, work_current, substance, severity, acsg_retain, acss_retain, acsi_retain, acsl_retain, acsf_retain)) %>%
  tbl_summary(
    missing = "no",
    by = time_injury_ex,
    type = list(
      c(age_current, substance, acsg_retain, acss_retain, acsi_retain, acsl_retain, acsf_retain) ~ "continuous",
      c(work_current, severity) ~ "categorical"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)"),
    label = list(
      age_current ~ "Age (years)",
      time_injury_ex ~ "Early/Late Recovery",
      work_current ~ "Employment status",
      substance ~ "Substance use score",
      severity ~ "Severity of Injury",
      acsg_retain ~ "Global ACS",
      acss_retain ~ "Social ACS",
      acsi_retain ~ "IADL ACS",
      acsl_retain ~ "Leisure ACS",
      acsf_retain ~ "Fitness ACS"
    )
  ) 


print(demo_table_time)   
```

```{r save new table time, echo=FALSE, include=FALSE}
#to save table to word doc
library(gt)
library(gtsummary)

gt_demo_table_time <- as_gt(demo_table_time)
   gtsave(gt_demo_table_time, filename = "demo_table_time.docx")
```


```{r counts of new groups, echo=FALSE, include=TRUE}
level_counts3 <- table(df_time3$time_injury_ex)

# Displaying the counts
print(level_counts3)
```
We see the counts of # participants in each group

### Global
Global ACS3 scores (ie, global re-engagement scores)
```{r global 3, echo=FALSE, include=TRUE}
group_by(df_time3, time_injury_ex) %>%
  summarise(
    count = n(),
    mean = mean(acsg_retain, na.rm = TRUE),
    sd = sd(acsg_retain, na.rm = TRUE)
  )
```

```{r  vis global 3, echo=FALSE, include=TRUE}
library("ggpubr")
ggboxplot(df_time3, x = "time_injury_ex", y = "acsg_retain",
          color = "time_injury_ex", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          order = c("Early", "Mid", "Later"),
          ylab = "Global Engagement", xlab = "Time Since Injury")
```

```{r vis global 3 to save, results='asis', echo=FALSE, include=FALSE}
library("ggpubr")

# Set global font to Times New Roman
theme_set(theme_gray(base_family = "Times New Roman"))

# Create the plot
plot <- ggline(df_time3, x = "time_injury_ex", y = "acsg_retain",
               add = c("mean_se", "jitter"),
               order = c("Early", "Mid", "Late")) +
        labs(x = "Time Since Injury", y = "Global Engagement", 
             face = "bold", family = "Times New Roman")

# Save the plot as a PNG file with DPI=300
ggsave("plot.png", plot, dpi = 300)
```
```{r vis global 3 again, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "acsg_retain",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "Global Engagement", xlab = "Time Since Injury")
```

```{r anova global extreme, echo=FALSE, include=TRUE}
res.aov <- aov(acsg_retain~time_injury_ex, data=df_time3)
summary(res.aov)
```

```{r lm global, echo=FALSE, include=TRUE}
model_timeinjury_ex <- lm(acsg_retain~age_current+time_injury_ex, data=df_time3)
summary(model_timeinjury_ex)
```
Controlling for age, we see a significant relationship between time since injury and global re engagement- specifically between early and later recovery

### Social
social ACS3 scores (ie, social re-engagement scores)
```{r Social 3, echo=FALSE, include=TRUE}
group_by(df_time3, time_injury_ex) %>%
  summarise(
    count = n(),
    mean = mean(acss_retain, na.rm = TRUE),
    sd = sd(acss_retain, na.rm = TRUE)
  )
```

```{r  vis Social 3, echo=FALSE, include=TRUE}
library("ggpubr")
ggboxplot(df_time3, x = "time_injury_ex", y = "acss_retain",
          color = "time_injury_ex", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          order = c("Early", "Mid", "Later"),
          ylab = "Social Engagement", xlab = "Time Since Injury")
```

```{r vis Social 3 again, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "acss_retain",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "Social Engagement", xlab = "Time Since Injury")
```

```{r anova social 3, echo=FALSE, include=TRUE}
res.aov <- aov(acss_retain~time_injury_ex, data=df_time3)
summary(res.aov)
```

```{r lm social 3, echo=FALSE, include=TRUE}
model_timeinjury_ex <- lm(acss_retain~age_current+time_injury_ex, data=df_time3)
summary(model_timeinjury_ex)
```

### IADL
IADL ACS3 scores (ie, IADL re-engagement scores)
```{r IADL 3, echo=FALSE, include=TRUE}
group_by(df_time3, time_injury_ex) %>%
  summarise(
    count = n(),
    mean = mean(acsi_retain, na.rm = TRUE),
    sd = sd(acsi_retain, na.rm = TRUE)
  )
```

```{r  vis IADL 3, echo=FALSE, include=TRUE}
library("ggpubr")
ggboxplot(df_time3, x = "time_injury_ex", y = "acsi_retain",
          color = "time_injury_ex", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          order = c("Early", "Mid", "Later"),
          ylab = "IADL Engagement", xlab = "Time Since Injury")
```

```{r vis IADL 3 again, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "acsi_retain",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "IADL Engagement", xlab = "Time Since Injury")
```

```{r anova IADL 3, echo=FALSE, include=TRUE}
res.aov <- aov(acsi_retain~time_injury_ex, data=df_time3)
summary(res.aov)
```

```{r lm IADL 3, echo=FALSE, include=TRUE}
model_timeinjury_ex <- lm(acsi_retain~age_current+time_injury_ex, data=df_time3)
summary(model_timeinjury_ex)
```
We see a significant difference between early and late groups with IADl engagement when controlling for age

### Leisure
Leisure ACS3 scores (ie, leisure re-engagement scores)
```{r Leisure 3, echo=FALSE, include=TRUE}
group_by(df_time3, time_injury_ex) %>%
  summarise(
    count = n(),
    mean = mean(acsl_retain, na.rm = TRUE),
    sd = sd(acsl_retain, na.rm = TRUE)
  )
```

```{r  vis Leisure 3, echo=FALSE, include=TRUE}
library("ggpubr")
ggboxplot(df_time3, x = "time_injury_ex", y = "acsl_retain",
          color = "time_injury_ex", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          order = c("Early", "Mid", "Later"),
          ylab = "Leisure Engagement", xlab = "Time Since Injury")
```

```{r vis Leisure 3 again, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "acsl_retain",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "Leisure Engagement", xlab = "Time Since Injury")
```

```{r anova Leisure 3, echo=FALSE, include=TRUE}
res.aov <- aov(acsl_retain~time_injury_ex, data=df_time3)
summary(res.aov)
```

```{r lm Leisure 3, echo=FALSE, include=TRUE}
model_timeinjury_ex <- lm(acsl_retain~age_current+time_injury_ex, data=df_time3)
summary(model_timeinjury_ex)
```
We see a significant difference between early and late groups with Leisure engagement when controlling for age

### Fitness
Fitness ACS3 scores (ie, fitness re-engagement scores)
```{r Fitness 3, echo=FALSE, include=TRUE}
group_by(df_time3, time_injury_ex) %>%
  summarise(
    count = n(),
    mean = mean(acsf_retain, na.rm = TRUE),
    sd = sd(acsf_retain, na.rm = TRUE)
  )
```

```{r  visualize Fitness 3, echo=FALSE, include=TRUE}
library("ggpubr")
ggboxplot(df_time3, x = "time_injury_ex", y = "acsg_retain",
          color = "time_injury_ex", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          order = c("Early", "Mid", "Later"),
          ylab = "Fitness Engagement", xlab = "Time Since Injury")
```

```{r vis Fitness 3 , echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "acsf_retain",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "Fitness Engagement", xlab = "Time Since Injury")
```

```{r anova Fitness 3, echo=FALSE, include=TRUE}
res.aov <- aov(acsf_retain~time_injury_ex, data=df_time3)
summary(res.aov)
```

```{r lm Fitness 3, echo=FALSE, include=TRUE}
model_timeinjury_ex <- lm(acsf_retain~age_current+time_injury_ex, data=df_time3)
summary(model_timeinjury_ex)
```


## Impact on Predictive Variables
This is exploratory and post hoc analysis- likely unable to report to avoid p-hacking, more for information gathering

### Correlations

```{r corr time injury, echo=FALSE, results='asis', fig.width=15,fig.height=15, include=TRUE}
library(ggplot2)
library(reshape2)
library(Hmisc)

time_variables <- c('time_injury', 'acsg_retain', 'acss_retain', 'acsi_retain', 'acsl_retain', 'acsf_retain', 'phys_health_index', 'emo_health_index', 'tbiqol_genconcern_tscore', 'spstotal', 'frsbe_total')

time_variables <- intersect(time_variables, colnames(df))  # Ensure selected variables are in the dataframe

time_variables_df <- df[, time_variables]

cor_matrix <- rcorr(as.matrix(time_variables_df),type = "spearman")$r
cor_matrix[upper.tri(cor_matrix)] <- NA
p_matrix <- rcorr(as.matrix(time_variables_df),type = "spearman")$P
p_matrix[is.na(p_matrix)]=.0000001
p_matrix[upper.tri(p_matrix)] <- NA

# Create a heatmap using ggplot2
ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value,2)), vjust = 1, size = 6) +  # Adjust size here
  geom_text(aes(label = psig), vjust = .25, size = 6) +  # Adjust size here
  scale_fill_gradient2(low = "purple", mid = "white", high = "orange", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name = "Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 20),  # Adjust size here
        axis.text.y = element_text(angle = 45, hjust = 1, size = 20),  # Adjust size here
        axis.title = element_text(size = 14),
        axis.ticks = element_line(size = 1)) +
  labs(caption = "<.05 = *, <.01 = **, <.001 = ***") +
  xlab("") +
  ylab("") +
  ggtitle("Correlation Matrix Personal Protective Factors Time Since Injury")

ggsave("corr_matrix_time.png", plot, width = 15, height = 15)

```

```{rsaveplot, include=FALSE, echo=FALSE}

```


### Self Regulation

```{r anova self-regulation, echo=FALSE, include=TRUE}
res.aov <- aov(frsbe_total~time_injury_ex, data=df_time3)
summary(res.aov)
```


```{r vis Frsbe 3, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "frsbe_total",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "Self-Regulation", xlab = "Time Since Injury")
```

### Physical Health

```{r anova phys health, echo=FALSE, include=TRUE}
res.aov <- aov(phys_health_index~time_injury_ex, data=df_time3)
summary(res.aov)
```


```{r vis phys, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "phys_health_index",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "Physical Health", xlab = "Time Since Injury")
```

### Emotional Health

```{r anova emo health, echo=FALSE, include=TRUE}
res.aov <- aov(emo_health_index~time_injury_ex, data=df_time3)
summary(res.aov)
```


```{r vis emo, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "emo_health_index",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Late"),
       ylab = "Physical Health", xlab = "Time Since Injury")
```

### General Cognition

```{r anova gen cog, echo=FALSE, include=TRUE}
res.aov <- aov(tbiqol_genconcern_tscore~time_injury_ex, data=df_time3)
summary(res.aov)
```


```{r vis gen cog, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "tbiqol_genconcern_tscore",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "Physical Health", xlab = "Time Since Injury")
```


### Social Support

```{r anova socialsupport, echo=FALSE, include=TRUE}
res.aov <- aov(tbiqol_genconcern_tscore~time_injury_ex, data=df_time3)
summary(res.aov)
```


```{r vis socialsupport, echo=FALSE, include=TRUE}
library("ggpubr")
ggline(df_time3, x = "time_injury_ex", y = "spstotal",
       add = c("mean_se", "jitter"),
       order = c("Early", "Mid", "Later"),
       ylab = "spstotal", xlab = "Time Since Injury")
```

## Cont Exploratory Analysis


Below is the comparison of t-values for step 3 and step 4 to see if the inclusion of time since injury significantly changed the contribution of each variable in the model. (not sure this is an appropriate way to report in paper, but wanted to see...)


```{r compare tvalue, echo=FALSE, include=TRUE}
# Variables of interest
variables <- c("age_current", "phys_health_index", "emo_health_index", "tbiqol_genconcern_tscore", "spstotal", "frsbe_total")

# Initialize a data frame to store z-test results
z_test_results <- data.frame(Variable = character(), z_score = numeric(), p_value = numeric(), stringsAsFactors = FALSE)

# Perform z-test for each variable
for (variable in variables) {
  # Extract t-values for the variable from both models
  t_value_step3 <- coef(summary(step3))[variable, "t value"]
  t_value_step4 <- coef(summary(step4))[variable, "t value"]
  
  # Compute the difference between t-values
  t_diff <- t_value_step3 - t_value_step4
  
  # Compute the standard error of the difference (assuming t-values are independent)
  se_diff <- sqrt(coef(summary(step3))[variable, "Std. Error"]^2 + coef(summary(step4))[variable, "Std. Error"]^2)
  
  # Compute z-score
  z_score <- t_diff / se_diff
  
  # Compute two-tailed p-value
  p_value <- 2 * pnorm(-abs(z_score))
  
  # Store z-test result in data frame
  z_test_results <- rbind(z_test_results, data.frame(Variable = variable, 
                                                     z_score = z_score, 
                                                     p_value = p_value))
}

# Print z-test results
print(z_test_results)


```

# Selection for gift cards

Create a sequence from 1 to 44
numbers <- 1:46

Randomly select 8 numbers
selected_numbers <- sample(numbers, 8)

Format the selected numbers with leading zeros
formatted_numbers <- sprintf("%03d", selected_numbers)

Print the selected numbers
print(formatted_numbers)

"020" "007" "006" "019" "024" "041" "013" "037"



